---
title: "part II"
date: "6/5/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

``` {r}
library(tidyverse)
library(zoo)
library(infer)
options(scipen = "999")

df <- read_csv("Oscars-demographics-DFE.csv")

skimr::skim(df)

```

 Which movie(s) won the most unique "Big 5" awards?
```{r}
df %>%
    select(movie, award) %>%
    unique() %>%
    count(movie,sort = TRUE)
```


# Of all actresses who have won the Best Actress award, what are is the most common first name?
```{r}
df %>%
  select(person, award) %>%
  filter(award == "Best Actress") %>%
  unique() %>%
  separate(person,
           c("first", "last")) %>%
  count(first, sort = TRUE) %>%
  mutate(first = fct_reorder(first,n)) %>%
  ggplot(aes(n, first)) +
  geom_col()
```



#What US State, or non-US country, has produced the most Oscar winners (for the awards in this dataset)?
```{r}
#NA value is New York City
df %>%
  select(birthplace, award, person) %>%
  unique() %>%
  separate(birthplace, c("city", "country_state"), sep = ",", extra = "drop", fill = "left") %>%
  replace(is.na(.), "NY") %>%
  count(country_state, sort = TRUE) %>%
  mutate(country_state = fct_reorder(country_state, n)) %>%
  filter(n > 10) %>%
  ggplot(aes(n, country_state)) +
  geom_col()
```



**thank you, Natalie O'Shea**
```{r}
# creating dummy vars for gender
df$men <- ifelse(df$award == "Best Supporting Actor" | df$award == "Best Actor", 1,0)

df$women <- ifelse(df$award == "Best Supporting Actress" | df$award == "Best Actress", "female", "male")

df_mod <- df %>%
  filter(award %in% c("Best Supporting Actor", "Best Actor", "Best Supporting Actress", "Best Actress")) %>%
  unique() %>%
  separate(date_of_birth, c("day", "month", "year"), sep = "-") %>%
  # add leading values to day and year if needed
  mutate(day = ifelse(nchar(day) < 2, paste0("0", day), day),
         year = ifelse(nchar(year) < 4, paste0("19", year), year)) %>% 
  # reunite into original column
  unite("date_of_birth", day:year, sep = "-") %>%
  # convert to dates and calculate age
  mutate(
    date_of_birth = dmy(date_of_birth),
    year_of_award = dmy(paste0("01-Feb-", year_of_award)),
    age = interval(date_of_birth, year_of_award) %/% years(1),
    women = as.factor(women)
  ) %>%
  select(women, age, year_of_award)

#linear model 

lm_mod <- lm(age ~ year(year_of_award) + women, data = df_mod)
summary(lm_mod)
```
**women are younger than men by an average of 10 years (p.val = 0.00)** 

##creating bootstrapped mean of propotion non white Oscar winners## 
```{r}
# confidence intervals

df$not_white <- ifelse(df$race_ethnicity != "White", 1, 0)

bt <- df %>%
  select(race_ethnicity, award, not_white) %>%
  specify(response = not_white) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "mean")

pct <- bt %>% get_confidence_interval(level = 0.95, type = "percentile")

ggplot(bt, aes(stat)) +
  geom_bar(position = "dodge" ) +
  shade_confidence_interval(endpoints = pct) +
  ggtitle("Average of non white oscar winners") +
  scale_x_continuous(labels = scales::percent_format())
```